---
title: "data visualization"
author: "Adelaide Robinson"
date: '2022-08-17'
output: html_document
---

```{r}
library(tidyverse)
library(here)
library(janitor)
library(patchwork)
library(ggrepel)
library(gghighlight)
library(paletteer)
library(ggExtra)
library(gapminder)
```

```{r}
space <- read_csv(here("data", "space_launches.csv"))
```

```{r}
space |> ggplot(aes(x = launch_year, y = type)) +
  geom_point(aes(color = agency)) +
   geom_text_repel(aes(label = agency)) + 
  labs(title = "Graph", x = "an amount of time", y = "a thing") + theme_dark() +
  theme(panel.grid.major.x = element_line(color = "blue"),
        panel.grid.minor.y = element_line(color = "green"),
        panel.background = element_rect(color = "purple", fil = "yellow"))

```

```{r}
ggsave(here("data", "mess.png"))
```

# Task 2

1.  Create a summary table of total annual greenhouse gas emissions (only from Emissions_mtCO2e column) by sector_general

```{r}
san_francisco <- read_csv(here("data", "San_Francisco_Communitywide_Greenhouse_Gas_Inventory.csv"))


```

```{r}

table <- san_francisco |> group_by(Sector_General) |> 
  summarize(sum(Emissions_mtCO2e, na.rm = TRUE))
```

Create a summary table of total annual greenhouse gas emissions (only from Emissions_mtCO2e column) by year and commodity type

```{r}
table_2 <- san_francisco |> 
  group_by(Calendar_Year, Commodity_Type) |> 
  summarize(sum(Emissions_mtCO2e, na.rm = TRUE))
  
```

Create a subset of the data that only contains observations from 2005 on, only for observations where `Sector_Detail2` contains the pattern \"PG&E\", then limit to columns `Calendar_Year`, `Sector_Detail2` and `Emissions_mtCO2e`.

```{r}

subset <- san_francisco |> 
  filter(Calendar_Year > 2005, str_detect(Sector_Detail2, pattern = "PG&E"))
 

```

```{r}

graph <- san_francisco |> 
  group_by(Calendar_Year, Sector_General) |> 
  summarize(total_emissions = sum(Emissions_mtCO2e, na.rm = TRUE))

graph |> ggplot(aes(x = Calendar_Year, y = total_emissions)) + geom_line(aes(color = Sector_General)) +
   labs(x = "Year",
       y = "Total Emissions (mtC02e)",
       title = "Total Emissions by Sector") +theme_minimal() + 
  theme(legend.position="bottom", panel.grid.major.y = element_blank())+ scale_color_brewer(palette="Dark2")

ggsave(here("data", "emissions.jpeg"), bg='transparent')``
```
